---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# causalsim

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The `causalsim` package uses a matrix containing the coefficients and standard deviations of the unique
independent components of a linear causal DAG to generate the marginal covariance matrix and to 
calculate the value of coefficients of linear models applied to a population generated by
the causal DAG.


## Installation

You can install the development version of causalsim like so:

``` r
remotes::install.github("gmonette/causalsim)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(causalsim)
## basic example code
```

